### 2023-03-09 manuscript.tex
Specifying equal contributions within the metadata [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4378679802

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/388ca7cf852b78a84a8e8b3411f1243976ed978b/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/388ca7cf852b78a84a8e8b3411f1243976ed978b}{SORTEE-Github-Hackathon/manuscript@388ca7c}
on March 9, 2023.

@@

  \textsuperscript{\protect\hyperlink{correspondence}{✉}}

@@

@@

@@

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/b7b98e0dba83c2c25ae7518de3f87bfe64fa235d}{SORTEE-Github-Hackathon/manuscript@b7b98e0}
on March 9, 2023.

@@

  \textsuperscript{\protect\hyperlink{correspondence}{✉}}†

@@

  ††

@@

  †

@@

† and †† --- These authors contributed equally to this work.
